### Load vsearch output
#### CT pollen
```{r include=FALSE}
ITS2 <- load_blast6("~/vsearchr/inst/extdata/ITS2_vsearch_CT.output/")
### Check for short but high ID alignments
ITS2_95 <- filter(ITS2, pident >= 95.0)
ggplot(ITS2_95, aes(length)) +
  geom_histogram()
```


### Load taxonomy tables
#### CT pollen
```{r include=FALSE}
ITS2_tax <- load_MTXA("~/vsearchr/inst/extdata/ITS2_CT_Amplicons.tax")
```


### Join vsearch output to taxonomy tables
#### CT pollen
```{r include=FALSE}
ITS2_join_95 <- tax_join(ITS2, ITS2_tax, min_id = 95.0, min_len = 300)
ITS2_eval_95 <- ITS2_join_95 %>% group_by(sample) %>%
  summarize(reads = n()) %>%
  arrange(sample)
```


### Tally genera by sample
#### CT pollen
```{r}
ITS2_tally <- tally_gen(ITS2_join_95)
```


### Add sample metadata and create consensus data sets
#### CT pollen
```{r include=FALSE}
### ITS2
ITS2_meta <- add_meta(ITS2_tally, "~/vsearchr/inst/extdata/CT_2015_key.csv")
genus_summary_ITS2 <- ITS2_meta %>%
  group_by(genus) %>%
  summarize(mol_freq = n(),
            max_prop = max(gen_prop))
ITS2_final <- left_join(ITS2_meta, genus_summary_ITS2, by = "genus")
```


### Plot data
##### ITS2 only
```{r}
ggplot(filter(ITS2_final, max_prop >= 0.05), aes(x = date, y = reorder(genus, mol_freq), fill = gen_prop)) +
  geom_tile(width = 6, color = "black") +
  scale_fill_gradient(low = "gray95", high = "purple") +
  theme_bw(6) +
  ylab("Genus") +
  xlab("Sample") +
  labs(fill = "Proportional\nabundance") +
  facet_grid(~site) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("~/vsearchr/inst/extdata/figures/ITS2_tileplot.pdf", width = 6.5, height = 4.5)
ggsave("~/vsearchr/inst/extdata/figures/ITS2_tileplot.png", width = 6.5, height = 4.5)
```

### Add microscopy data
```{r}
micro_dat <- read_csv("~/vsearchr/inst/extdata/micro_dat_v2.csv", col_names = TRUE) %>%
  rename(micro_vol_prop = prop_vol,
         micro_ct_prop = prop_count) %>%
  filter(genus != "undet") %>%
  #filter(micro_prop >= 0.001) %>%
  group_by(site, date, genus) %>%
  summarize(micro_vol_prop = sum(micro_vol_prop),
            micro_ct_prop = sum(micro_ct_prop))
CT_genus_summary_micro <- micro_dat %>%
  group_by(genus) %>%
  summarize(micro_freq = n(),
            max_vol_prop = max(micro_vol_prop),
            max_ct_prop = max(micro_ct_prop))
CT_micro_join <- left_join(micro_dat, CT_genus_summary_micro, by = "genus") %>%
  add_meta_micro("~/vsearchr/inst/extdata/CT_2015_key.csv") %>%
  na.omit()
```

### Pull out genus list to add traits
```{r}

ITS2_final_genera <- ungroup(ITS2_final) %>%
  select(genus) %>%
  unique()

micro_genera <- ungroup(micro_dat) %>%
  select(genus) %>%
  unique()

genus_list <- full_join(ITS2_final_genera, micro_genera, by = "genus")

#write_csv(genus_list, "~/vsearchr/inst/extdata/genus_list.csv")

genus_traits <- read_csv("~/vsearchr/inst/extdata/genus_traits.csv", col_names = TRUE)

ITS2_final_traits <- inner_join(ITS2_final, genus_traits, by = "genus") 

ggplot(filter(ITS2_final_traits), aes(x = form, y = gen_prop, fill = form)) +
  geom_bar(stat = "identity")
```

### Check whether my Genbank reference libs are missing any genera found in the micro data
```{r}
micro_anti_ITS2 <- anti_join(micro_dat, ITS2_tax, by = "genus") %>%
  ungroup() %>%
  select(genus) %>%
  unique()
```

### Join micro and metabarcoding data
```{r}
mol_dat <- ITS2_final %>% ungroup() %>%
  select(sample, site, date, genus, gen_prop, max_prop, mol_freq)

shared_sitedates <- inner_join(CT_micro_join, mol_dat, by = c("site", "date")) %>%
  select(site, date) %>%
  unique()

### join
micromol_dat <- full_join(mol_dat, CT_micro_join, by = c("sample", "site", "date", "genus")) %>%
  semi_join(shared_sitedates, by = c("site", "date")) %>%
  replace_na(list(gen_prop = 0, micro_vol_prop = 0, micro_ct_prop = 0, mol_freq = 0, micro_freq = 0)) %>%
  mutate(shared = case_when(
  gen_prop == 0 & micro_ct_prop > 0 ~ "micro_only",
  gen_prop > 0 & micro_ct_prop == 0 ~ "mol_only",
  gen_prop > 0 | micro_ct_prop > 0 ~ "shared"),
  shared_log = case_when(
    shared == "shared" ~ 1,
    shared != "shared" ~ 0)) %>%
  select(sample, site, date, genus, gen_prop, max_prop, micro_vol_prop, micro_ct_prop, shared, shared_log, mol_freq, micro_freq)

micromol_dat_genus_summary <- micromol_dat %>%
  group_by(genus) %>%
  summarize(max_micro_ct = max(micro_ct_prop),
            max_micro_vol = max(micro_vol_prop))

micromol_dat_final <- left_join(micromol_dat, micromol_dat_genus_summary, by = "genus")
write_csv(micromol_dat_final, "~/Desktop/micro_mol_comparison_ITS2.csv")
```

### Plot microscopy data
```{r}
ggplot(filter(CT_micro_join, max_vol_prop >= 0.05), aes(x = date, y = reorder(genus, micro_freq), fill = micro_vol_prop)) +
  geom_tile(width = 6, color = "black") +
  scale_fill_gradient(low = "gray95", high = "purple") +
  theme_bw(9) +
  ylab("Genus") +
  xlab("Sample") +
  labs(fill = "Proportional\nabundance") +
  facet_grid(~site) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("~/vsearchr/inst/extdata/figures/micro_tileplot.pdf", width = 7.5, height = 4.5)
ggsave("~/vsearchr/inst/extdata/figures/micro_tileplot.png", width = 7.5, height = 4.5)
```

### Comparing metabarcoding and microscopy
```{r}
### Bar plot of detections
# ITS2 only
ggplot(micromol_dat_final, aes(x = shared, fill = shared)) +
  geom_bar() +
  theme_gray(18) +
  scale_fill_discrete(name = NULL, labels = c("microscopy", "metabarcoding", "both")) +
  scale_x_discrete(labels = c("microscopy", "metabarcoding", "both")) +
  ylab("detections") +
  xlab(NULL)

ggplot(filter(micromol_dat_final, gen_prop >= 0.05 | micro_vol_prop >= 0.05), 
       aes(x = shared, fill = shared)) +
  geom_bar() +
  theme_gray(14) +
  scale_fill_discrete(name = NULL, labels = c("microscopy", "metabarcoding", "both")) +
  scale_x_discrete(labels = c("microscopy", "metabarcoding", "both")) +
  ylab("detections") +
  xlab(NULL)
ggsave("~/vsearchr/inst/extdata/figures/micro_vs_mol_aggregate.pdf", width = 6.5, height = 4.5)
ggsave("~/vsearchr/inst/extdata/figures/micro_vs_mol_aggregate.png", width = 6.5, height = 4.5)

### Scatter plot of abundances
#### Grain count
ggplot(micromol_dat_final, aes(x = sqrt(gen_prop), y = sqrt(micro_ct_prop), color = shared)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm") +
  theme_gray(14) +
  geom_abline(intercept = 0, slope = 1, color = "gray40", linetype = "dashed") +
  scale_color_discrete(name = NULL, labels = c("microscopy", "metabarcoding", "both")) +
  xlab(expression(sqrt("read count"))) +
  ylab(expression(sqrt("grain count")))
ggsave("~/vsearchr/inst/extdata/figures/micro_vs_mol_abundance_ct.pdf", width = 6.5, height = 4)
ggsave("~/vsearchr/inst/extdata/figures/micro_vs_mol_abundance_ct.png", width = 6.5, height = 4)

#### Volume
ggplot(micromol_dat_final, aes(x = sqrt(gen_prop), y = sqrt(micro_vol_prop), color = shared)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm") +
  theme_gray(14) +
  geom_abline(intercept = 0, slope = 1, color = "gray40", linetype = "dashed") +
  scale_color_discrete(name = NULL, labels = c("microscopy", "metabarcoding", "both")) +
  xlab(expression(sqrt("read count"))) +
  ylab(expression(sqrt("grain volume")))
ggsave("~/vsearchr/inst/extdata/figures/micro_vs_mol_abundance_vol.pdf", width = 6.5, height = 4)
ggsave("~/vsearchr/inst/extdata/figures/micro_vs_mol_abundance_vol.png", width = 6.5, height = 4)

### Scatter plot of frequencies
ggplot(micromol_dat_final, aes(mol_freq, micro_freq, color = shared)) +
  geom_point(alpha = 0.2) +
  theme_gray(14) +
  geom_abline(intercept = 0, slope = 1, color = "gray40", linetype = "dashed") +
  scale_color_discrete(name = NULL, labels = c("microscopy", "metabarcoding", "both")) +
  stat_smooth(method = "lm")
ggsave("~/vsearchr/inst/extdata/figures/micro_vs_mol_freq.pdf", width = 6.5, height = 4)
ggsave("~/vsearchr/inst/extdata/figures/micro_vs_mol_freq.png", width = 6.5, height = 4)


### Grouped barplot of agreement
micromol_long <- micromol_dat_final %>% 
  select(sample, site, date, genus, gen_prop, micro_vol_prop) %>%
  gather(metric, value, -sample, -site, -date, -genus)

micromol_long_major <- micromol_dat_final %>% 
  filter(gen_prop >= 0.05 | micro_ct_prop >= 0.05) %>%
  select(sample, site, date, genus, gen_prop, micro_vol_prop) %>%
  gather(metric, value, -sample, -site, -date, -genus)

ggplot(micromol_long_major, aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy")) +
  ylab("proportional abundance") +
  facet_grid(sample ~ .)
ggsave("~/vsearchr/inst/extdata/figures/C0820.pdf", width = 6.5, height = 6.5)


ggplot(filter(micromol_long_major, sample == "CT1"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_8/20") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/C0820.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT2"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_9/17") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/B0917.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT3"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("A_7/27") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/A0727.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT4"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("A_6/12") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/A0612.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT5"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_7/8") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/B0708.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT6"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("C_7/16") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/C0716.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT7"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("A_8/31") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/A0831.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT8"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_9/3") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/C0903.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT9"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("C_9/10") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/C0910.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT10"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_9/2") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/B0902.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT11"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_7/15") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/B0715.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT12"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_7/2") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/C0702.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT13"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("B_5/27") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/B0527.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT14"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("A_7/7") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/A0707.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT15"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("A_5/13") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/A0513.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT16"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_6/4") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/C0604.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT17"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("C_8/13") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/C0813.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT18"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_7/23") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/C0723.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT19"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("A_8/10") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/A0810.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT20"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_8/13") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/B0813.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT21"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("B_6/17") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/B0617.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT22"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("B_9/23") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/B0923.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT23"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("A_6/18") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/A0618.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT24"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_6/11") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/C0611.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT25"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_5/28") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/C0528.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT26"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_6/30") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/B0630.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT27"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("B_6/24") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/B0624.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT28"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("A_5/22") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/A0522.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT29"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("A_9/14") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/A0914.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT30"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("A_9/21") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/A0921.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT31"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_6/10") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/B0610.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT32"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("A_8/3") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/A0803.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT33"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_8/25") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/B0825.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT34"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("A_5/29") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/A0529.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT35"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_7/22") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/B0722.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT36"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_8/7") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance") 
ggsave("~/vsearchr/inst/extdata/figures/C0807.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT37"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_6/25") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/C0625.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT38"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("B_8/4") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/B0804.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT39"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_7/30") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/C0730.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT40"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_8/19") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/C0819.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT41"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("B_6/3") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/B0603.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT42"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("C_9/18") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/C0918.pdf", width = 6.5, height = 6.5)

# ggplot(filter(micromol_long_major, sample == "CT43"), aes(x = genus, y = value, fill = metric)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   ggtitle("A_7/13") +
#   geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
#     scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
#   ylab("proportional abundance") +
# ggsave("~/vsearchr/inst/extdata/figures/A0713.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT44"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("A_6/26") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/A0626.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT45"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_8/28") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/C0828.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT46"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("C_6/19") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/C0619.pdf", width = 6.5, height = 6.5)

ggplot(filter(micromol_long_major, sample == "CT47"), aes(x = genus, y = value, fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("A_7/20") +
  #geom_abline(intercept = 0.05, slope = 0, color = "gray40", linetype = "dashed") +
  scale_fill_discrete(name = NULL, labels = c("metabarcoding", "microcopy (vol)")) +
  ylab("proportional abundance")
ggsave("~/vsearchr/inst/extdata/figures/A0720.pdf", width = 6.5, height = 6.5)


### Linear model of abundance
lm1 <- lm(sqrt(micro_vol_prop) ~ sqrt(gen_prop), data = filter(micromol_dat_final, shared_log == 1))
summary(lm1)
plot(lm1)


### Count proportion vs volume proportion
ggplot(micromol_dat_final, aes(micro_ct_prop, micro_vol_prop)) +
  geom_point() +
  stat_smooth(method = "lm")

ggplot(micromol_dat_final, aes(sqrt(micro_ct_prop), sqrt(micro_vol_prop))) +
  geom_point() +
  stat_smooth(method = "lm") +
  xlab("sqrt(count)") +
  ylab("sqrt(volume)")
ggsave("~/Desktop/count_vs_volume.pdf")

# Unique genera detected
micro_genera_major <- tibble(unique(filter(micro_dat, micro_vol_prop >= 0.05)$genus)) %>% rename(genus = 1)
mol_genera_major <- tibble(unique(filter(ITS2_final, gen_prop >= 0.05)$genus)) %>% rename(genus = 1)
shared_genera_major <- inner_join(micro_genera_major, mol_genera_major)

```
